Miniproject - Algebraic Geometry

### 2022-01-19 Algebraic geometry/submission.tex
Finalized alg geo
Added note above the mistake I made

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{listings}
\usepackage{stmaryrd}
\usepackage[style=english]{csquotes}
\usepackage[language=english, backend=biber, style=alphabetic, sorting=nyt]{biblatex}
\usepackage{tikz}

@@

\title{Miniproject - Algebraic Geometry}
\author{Student Number: 1462479}
\date{19.02.2021}

@@

\section{Part I}
First of all, I will include here a more formal definition of the exterior product, which is required for rigorous proofs later on.
\begin{definition}
    Define the $d$-th exterior power of $V$ as a quotient of the free vector space of $B \times ... \times B$ as follows
    \begin{align*}
        \extpow^d V := \mathrm{Fr}\Bigl(\bigtimes_{i = 1}^d B\Bigr) \ \bigm/ \ U
    \end{align*}
    where
    \begin{align*}
        U = \vspan \bigl\{ (v_1, ..., v_d) + (v_1, ..., v_{i - 1}, v_{i + 1}, v_i, v_{i + 2}, ..., v_d) \ \bigm| \ v_1, ..., v_d \in B, 1 \leq i < d \bigr\}
    \end{align*}
    Consider also the map
    \begin{equation*}
        \wedge: \bigtimes_{i = 1}^d V \to \extpow^d V, \quad \Bigl( \sum_{i = 1}^n \lambda_{1i} b_i, ..., \sum_{i = 1}^n \lambda_{di} b_i \Bigr) \mapsto \sum_{1 \leq i_1, ..., i_d \leq n} \lambda_{1i_1} ... \lambda_{di_d} (b_{i_1}, ..., b_{i_d})
    \end{equation*}
    and use the notation $v_1 \wedge ... \wedge v_d$ to denote the image of $(v_1, ..., v_d)$ under this map.
\end{definition}
First of all, we show some basic properties of the exterior product.
It is straightforward to see that the exterior product is multilinear, i.e. $v_1 \wedge ... \wedge (v_i + v'_i) \wedge ... \wedge v_d = (v_1 \wedge ... \wedge v_d) + (v_1 \wedge ... \wedge v'_i \wedge ... \wedge v_d)$.
More interesting are the following properties.
\begin{lemma}
    \label{prop:basic_properties_exterior_product}
    Let $v_1, ..., v_d \in V$. Have for $\pi \in S_d$ that
    \begin{equation*}
        v_{\pi(1)} \wedge ... \wedge v_{\pi(k)} = \sgn(\pi) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
    Furthermore if $v_i = v_j$ for some $i \neq j$, then
    \begin{equation*}
        v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
\end{lemma}
\begin{proof}
    Clearly the vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ span $\extpow^d V$.
    So let
    \begin{equation*}
        u = \sum_{i_1, ..., i_{j - 1}} \lambda_{i_1, ..., i_{j - 1}} (b_1 \wedge ... \wedge b_{j - 1}), \quad w = \sum_{i_1, ..., i_{d - j - 1}} \mu_{i_1, ..., i_d} (b_{i_1} \wedge ... \wedge b_{d - j - 1})
    \end{equation*}
    be arbitrary vectors in $\extpow^{j - 1} V$ resp. $\extpow^{d - j - 1} V$ for some $1 \leq j \leq d - 1$.
    Note that for $v = \sum \tau_i b_i, v' = \sum \tau'_i b_i \in V$ have then
    \begin{align*}
        &(u \wedge v \wedge v' \wedge w) + (u \wedge v' \wedge v \wedge w) = \sum_{i_1, ..., i_{j - 1}, i_{j + 2}, ..., i_d} \ \sum_{0 \leq i_j, i_{j + 1} \leq n} \lambda_{i_1, ..., i_{j - 1}} \mu_{i_{j + 2}, ..., i_d} \tau_{i_j} \tau'_{i_{j + 1}} \\
        &\Bigl(\underbrace{\bigl( b_{i_1} \wedge ... \wedge b_{i_j} \wedge b_{i_{j + 1}} \wedge ... \wedge b_{i_d}\bigr) + \bigl( b_{i_1} \wedge ... \wedge b_{i_{j - 1}} \wedge b_{i_{j + 1}} \wedge b_{i_j} \wedge b_{i_{j + 2}} \wedge ... \wedge b_{i_d} \bigr)}_{= 0 \ \text{as it is an element of the space $U$}} \Bigl) \\
        &= 0
    \end{align*}
    Hence
    \begin{equation*}
        u \wedge v \wedge v' \wedge w = -(u \wedge v' \wedge v \wedge w)
    \end{equation*}

@@

\begin{lemma}[Question (a)]
    Let $\dim(V) \leq 3$. Then every element of $\extpow^k(V)$ is decomposable.
\end{lemma}
\begin{proof}
    Now let $v_1, v_2, v_3$ be a set of generators of $V$.
    Consider $u_1 = \sum \lambda_i v_i, u_2 = \sum_i \mu_i v_i, u_3 = \sum_i \rho_i v_i$.
    Then by applying Lemma~\ref{prop:basic_properties_exterior_product}, we see that 
    \begin{align*}
        u_1 \wedge u_2 =& \sum_{i, j} \ \lambda_i \mu_j (\underbrace{v_i \wedge v_j}_{\mathclap{\text{$= 0$ if $i = j$}}}) = \sum_{i < j} \lambda_i \mu_j (v_i \wedge v_j) + \sum_{i > j} \lambda_i \mu_j (v_i \wedge v_j) \\
        =& \sum_{i < j} (\lambda_i \mu_j - \lambda_j \mu_i)(v_i \wedge v_j) = \alpha (v_1 \wedge v_2) + \beta (v_1 \wedge v_3) + \gamma (v_2 \wedge v_3) \\
        =& \begin{cases}
            (\beta v_1 + \gamma v_2) \wedge (\frac \alpha \beta v_2 + v_3) & \text{if $\beta \neq 0$} \\
            (\alpha v_1 - \gamma v_3) \wedge v_2 & \text{otherwise}
        \end{cases}
    \end{align*}
    and
    \begin{align*}
        u_1 \wedge u_2 \wedge u_3 =& \sum_{i, j, l} \ \lambda_i \mu_j \rho_l (\underbrace{v_i \wedge v_j \wedge v_l}_{\mathclap{\text{$= 0$ unless $i, j, l$ pairwise distinct}}}) \\
        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} (v_{\pi(1)} \wedge v_{\pi(2)} \wedge v_{\pi(3)}) \\
        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi) (v_1 \wedge v_2 \wedge v_3) \\
        =& (v_1 \wedge v_2 \wedge v_3) \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi)
    \end{align*}
    are decomposable.
    Further, it is easy to see from Lemma~\ref{prop:basic_properties_exterior_product} that $\extpow^k(V) = \{ 0 \}$ for $k \geq 4$, which is trivially decomposable.
\end{proof}

@@

    For the other direction, let $v_1, ..., v_d$ be linearly independent.
    Clearly, we can extend them to a basis $v_1, ..., v_n$ of $V$.
    We then see that there is a matrix $A = (a_{ij}) \in \GL_n(k)$ with $v_i = \sum_j a_{ij} b_j$.
    So by Lemma~\ref{prop:linear_transform_extpow} have
    \begin{equation*}
        v_1 \wedge ... \wedge v_n = \underbrace{\det(A)}_{\neq 0} (b_1 \wedge ... \wedge b_n) \neq 0
    \end{equation*}
\end{proof}
Now we can see that in general, the exterior product contains not decomposable elements.
\begin{lemma}[Question (c)]
    \label{prop:characterization_decomposable_d_even}
    Let $d$ be even.
    An element $\omega \in \extpow^d V$ is decomposable if and only if $\omega \wedge \omega \in \extpow^{2d} V$ is zero.
\end{lemma}
\begin{proof}
    The direction $\Rightarrow$ even holds generally. Assume $\omega = v_1 \wedge ... \wedge v_d$.
    Then
    \begin{equation*}
        \omega \wedge \omega = v_1 \wedge ... \wedge v_d \wedge v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
    by Lemma~\ref{prop:basic_properties_exterior_product}. 
    The other direction is more interesting.

    Let $\omega = v_1 + ... + v_t$ for linearly independent decomposable vectors $v_i \in \extpow^d V$.
    Then
    \begin{align*}
        0 =& \omega \wedge \omega = \sum_{i, j} v_i \wedge v_j = \sum_{i < j} (v_i \wedge v_j) + (v_j \wedge v_i) \\
        \overset{*}{=}& \sum_{i < j} 2(v_i \wedge v_j) = 2\sum_i v_i \wedge \Bigl( \sum_{j > i} v_j \Bigr)
    \end{align*}
    Here we used for $*$ that the reversing permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has even parity, i.e. $\sgn(\cdot) = 1$ (since $d$ is even).

@@

    By Lemma~\ref{prop:leading_term_ideal_grassmanian} we see that
    \begin{equation*}
        \mathrm{lt}(f)^d = \mathrm{lt}(f^d) \in J = \langle x_{i, v} x_{j, u} \ | \ i < j < u < v \rangle
    \end{equation*}
    Hence
    \begin{equation*}
        \mathrm{lt}(f)^d \equiv t x_{i, v} x_{j, u}
    \end{equation*}
    for some $i < j < u < v$ and some monomial $t \in R$.
    Clearly $x_{i, v} \perp x_{j, u}$, and it follows that
    \begin{equation*}
        x_{i, v} x_{j, u} \divides \mathrm{lt}(f)
    \end{equation*}
    Now consider
    \begin{equation*}
        f' := f - \frac {\mathrm{lt}(f)} {x_{i, v} x_{j, u}} (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v}) \in R
    \end{equation*}
    Clearly $\mathrm{lt}(f') \prec \mathrm{lt}(f)$ as $x_{i, v} x_{j, v}, x_{i, j} x_{u, v} \prec x_{i, v} x_{j, u} \equiv \mathrm{lt}(f)$.
    Furthermore
    \begin{equation*}
        (f')^d = \sum_{l = 0}^d {d \choose i} f^i (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})^{d - i} \in I
    \end{equation*}
    so by induction hypothesis, find that $f' \in I$.
    It follows that also
    \begin{equation*}
        f = f'  - \frac {\mathrm{lt}(f)} {x_{i, v} x_{j, u}} (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v}) \in I
    \end{equation*}
    and the claim is shown.
\end{proof}
Now we have to study the structure of monomials generating $J = \langle x_{i, v} x_{j, u} \ | \ i < j < u < v \rangle$.
At first glance, this seemed to me to be much simpler than the above, but in fact it turns out not to be, as there is some subtle combinatorial structure involved.
Hence, we will first introduce the combinatorial framework in which we will work now.
\begin{definition}
    Consider the graph $G_n = (V_n, E_n)$ where $V_n = \{ (i, j) \ | \ 0 \leq i < j \leq n \}$ and
    \begin{equation*}
        E_n = \{ \{ (i, v), (j, u) \} \ | \ 0 \leq i < j < u < v \leq n \}
    \end{equation*}
    Let further
    \begin{equation*}
        s_n(d) := |\{ I \subseteq V_n \ | \ I \ \text{independent set of size $d$}\}|
    \end{equation*}
\end{definition}
It might be possible to see from the definition how independent sets in this graph are connected to monomials in $J$.
If not, the connection is explained in the proof of the next theorem.
\begin{proposition}
    Let $d$ be the largest integer such that $s_n(d) \neq 0$, i.e. the size of the largest independent set in $G_n$.
    Then
    \begin{equation*}
        \dim(\Gr(2, n)) = d - 1
    \end{equation*}
    and
    \begin{equation*}
        \deg(\Gr(2, n)) = s_n(d)
    \end{equation*}
\end{proposition}
\begin{proof}
    The idea is to apply Macaulay's basis theorem to get information about the Hilbert function of $\Gr(2, n)$.
    To this end, observe that all the monomials generating $\mathrm{lt}(\I(\Gr(2, n)))$ are square-free.
    Hence, we can partition all monomials not in $\mathrm{lt}(\I(\Gr(2, n)))$ into sets depending on which variables occur in them.
    Doing this shows that leading coefficient of the Hilbert polynomial depends only on the groups with the maximal count of monomials.
    These monomials then form a maximal independent set in $G_n$, which allows us to relate degree and dimension of $\Gr(2, n)$ to $s_n(d)$.

>>>>

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{listings}
\usepackage[normalem]{ulem}
\usepackage[language=english, backend=biber, style=alphabetic, sorting=nyt]{biblatex}
\usepackage{tikz}

@@

\title{Miniproject - Algebraic Geometry}
\author{Candidate Number: 1059926}
\date{19.02.2021}

@@

\section{Part I}
First of all, I will include here a more formal definition of the exterior product, which is required for rigorous proofs later on.
\begin{definition}
    Define the $d$-th exterior power of $V$ as a quotient of the free vector space of $B \times ... \times B$ as follows
    \begin{align*}
        \extpow^d V := \mathrm{Fr}\Bigl(\bigtimes_{i = 1}^d B\Bigr) \ \bigm/ \ U
    \end{align*}
    where
    \begin{align*}
        U = \vspan \bigl\{ (v_1, ..., v_d) + (v_1, ..., v_{i - 1}, v_{i + 1}, v_i, v_{i + 2}, ..., v_d) \ \bigm| \ v_1, ..., v_d \in B, 1 \leq i < d \bigr\}
    \end{align*}
    Consider also the map
    \begin{equation*}
        \wedge: \bigtimes_{i = 1}^d V \to \extpow^d V, \quad \Bigl( \sum_{i = 1}^n \lambda_{1i} b_i, ..., \sum_{i = 1}^n \lambda_{di} b_i \Bigr) \mapsto \sum_{1 \leq i_1, ..., i_d \leq n} \lambda_{1i_1} ... \lambda_{di_d} (b_{i_1}, ..., b_{i_d})
    \end{equation*}
    and use the notation $v_1 \wedge ... \wedge v_d$ to denote the image of $(v_1, ..., v_d)$ under this map.
\end{definition}
First of all, we show some basic properties of the exterior product.
It is straightforward to see that the exterior product is multilinear, i.e. $v_1 \wedge ... \wedge (v_i + v'_i) \wedge ... \wedge v_d = (v_1 \wedge ... \wedge v_d) + (v_1 \wedge ... \wedge v'_i \wedge ... \wedge v_d)$.
More interesting are the following properties.
\begin{lemma}
    \label{prop:basic_properties_exterior_product}
    Let $v_1, ..., v_d \in V$. Have for $\pi \in S_d$ that
    \begin{equation*}
        v_{\pi(1)} \wedge ... \wedge v_{\pi(k)} = \sgn(\pi) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
    Furthermore if $v_i = v_j$ for some $i \neq j$, then
    \begin{equation*}
        v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
\end{lemma}
\begin{proof}
    Clearly the vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ span $\extpow^d V$.
    So let
    \begin{equation*}
        u = \sum_{i_1, ..., i_{j - 1}} \lambda_{i_1, ..., i_{j - 1}} (b_1 \wedge ... \wedge b_{j - 1}), \quad w = \sum_{i_1, ..., i_{d - j - 1}} \mu_{i_1, ..., i_d} (b_{i_1} \wedge ... \wedge b_{d - j - 1})
    \end{equation*}
    be arbitrary vectors in $\extpow^{j - 1} V$ resp. $\extpow^{d - j - 1} V$ for some $1 \leq j \leq d - 1$.
    Note that for $v = \sum \tau_i b_i, v' = \sum \tau'_i b_i \in V$ have then
    \begin{align*}
        &(u \wedge v \wedge v' \wedge w) + (u \wedge v' \wedge v \wedge w) = \sum_{i_1, ..., i_{j - 1}, i_{j + 2}, ..., i_d} \sum_{0 \leq i_j, i_{j + 1} \leq n} \lambda_{i_1, ..., i_{j - 1}} \mu_{i_{j + 2}, ..., i_d} \tau_{i_j} \tau'_{i_{j + 1}} \\
        &\Bigl(\underbrace{\bigl( b_{i_1} \wedge ... \wedge b_{i_j} \wedge b_{i_{j + 1}} \wedge ... \wedge b_{i_d}\bigr) + \bigl( b_{i_1} \wedge ... \wedge b_{i_{j - 1}} \wedge b_{i_{j + 1}} \wedge b_{i_j} \wedge b_{i_{j + 2}} \wedge ... \wedge b_{i_d} \bigr)}_{= 0 \ \text{as it is an element of the space $U$}} \Bigl) \\
        &= 0
    \end{align*}
    Hence
    \begin{equation*}
        u \wedge v \wedge v' \wedge w = -(u \wedge v' \wedge v \wedge w)
    \end{equation*}

@@

\begin{lemma}[Question (a)]
    Let $\dim(V) \leq 3$. Then every element of $\extpow^k(V)$ is decomposable.
\end{lemma}
I did not include the proof here, as it contained a slight mistake.

@@

    For the other direction, let $v_1, ..., v_d$ be linearly independent.
    Clearly, we can extend them to a basis $v_1, ..., v_n$ of $V$.
    We then see that there is a matrix $A = (a_{ij}) \in \GL_n(k)$ with $v_i = \sum_j a_{ij} b_j$.
    So by Lemma~\ref{prop:linear_transform_extpow} have
    \begin{equation*}
        v_1 \wedge ... \wedge v_n = \underbrace{\det(A)}_{\neq 0} (b_1 \wedge ... \wedge b_n) \neq 0
    \end{equation*}
\end{proof}
Sadly, I have made a crucial mistake in my solution to the next question.
This mistake boils down to the fact that in general
\begin{equation*}
    \extpow^{2d} V \not\cong \extpow^2 \extpow^d V
\end{equation*}
Observe e.g. that $\dim \extpow^4 k^3 = 0$ but $\dim \extpow^2 \extpow^2 k^3 = 3$.
In fact, the next lemma only holds for $d = 2$.
\begin{lemma}[Question (c)]
    \label{prop:characterization_decomposable_d_even}
    Let $d$ be \sout{even} two.
    An element $\omega \in \extpow^d V$ is decomposable if and only if $\omega \wedge \omega \in \extpow^{2d} V$ is zero.
\end{lemma}
\begin{proof}
    The direction $\Rightarrow$ even holds generally. Assume $\omega = v_1 \wedge ... \wedge v_d$.
    Then
    \begin{equation*}
        \omega \wedge \omega = v_1 \wedge ... \wedge v_d \wedge v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
    by Lemma~\ref{prop:basic_properties_exterior_product}. 
    The other direction is more interesting.

    Let $\omega = v_1 + ... + v_t$ for linearly independent decomposable vectors $v_i \in \extpow^d V$.
    Then
    \begin{align*}
        0 =& \omega \wedge \omega = \sum_{i, j} v_i \wedge v_j = \sum_{i < j} (v_i \wedge v_j) + (v_j \wedge v_i) \\
        \overset{*}{=}& \sum_{i < j} 2(v_i \wedge v_j) = 2\sum_i v_i \wedge \Bigl( \sum_{j > i} v_j \Bigr)
    \end{align*}
    Here we used for $*$ that the reversing permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has even parity, i.e. $\sgn(\cdot) = 1$ (since $d$ is even)
    \footnote{Here is the mistake: Here and further down, we consider $v_i \wedge v_j \in \extpow^2 \extpow^d V$, and so the permutation is just $(1 \ 2)$, which clearly has odd parity.
    If we would consider $v_i \wedge v_j \in \extpow^{2d} V$, this step seems to work out, but below, we then cannot apply Lemma~\ref{prop:extpow_zero_iff_independent} and Lemma~\ref{prop:subspace_closed}}.

@@

    By Lemma~\ref{prop:leading_term_ideal_grassmanian} we see that
    \begin{equation*}
        \mathrm{lt}(f)^d = \mathrm{lt}(f^d) \in J = \langle x_{i, v} x_{j, u} \ | \ i < j < u < v \rangle
    \end{equation*}
    Hence
    \begin{equation*}
        \mathrm{lt}(f)^d \equiv t x_{i, v} x_{j, u}
    \end{equation*}
    for some $i < j < u < v$ and some monomial $t \in R$.
    Clearly $x_{i, v} \perp x_{j, u}$, and it follows that
    \begin{equation*}
        x_{i, v} x_{j, u} \divides \mathrm{lt}(f)
    \end{equation*}
    Now consider
    \begin{equation*}
        f' := f - \frac {\mathrm{lt}(f)} {x_{i, v} x_{j, u}} (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v}) \in R
    \end{equation*}
    Clearly $\mathrm{lt}(f') \prec \mathrm{lt}(f)$ as $x_{i, v} x_{j, v}, x_{i, j} x_{u, v} \prec x_{i, v} x_{j, u} \equiv \mathrm{lt}(f)$.
    Furthermore
    \begin{equation*}
        (f')^d = \sum_{l = 0}^d {d \choose i} f^i (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})^{d - i} \in I
    \end{equation*}
    so by induction hypothesis, find that $f' \in I$.
    It follows that also
    \begin{equation*}
        f = f'  - \frac {\mathrm{lt}(f)} {x_{i, v} x_{j, u}} (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v}) \in I
    \end{equation*}
    and the claim is shown.
\end{proof}
Now we have to study the structure of monomials generating $J = \langle x_{i, v} x_{j, u} \ | \ i < j < u < v \rangle$.
At first glance, this seemed to me to be much simpler than the above, but in fact it turns out not to be, as there is some subtle combinatorial structure involved.
Hence, we will first introduce the combinatorial framework in which we will work now.
\begin{definition}
    Consider the graph $G_n = (V_n, E_n)$ where $V_n = \{ (i, j) \ | \ 0 \leq i < j \leq n \}$ and
    \begin{equation*}
        E_n = \{ \{ (i, v), (j, u) \} \ | \ 0 \leq i < j < u < v \leq n \}
    \end{equation*}
    Let further
    \begin{equation*}
        s_n(d) := |\{ I \subseteq V_n \ | \ I \ \text{independent set of size $d$}\}|
    \end{equation*}
\end{definition}
It might be possible to see from the definition how independent sets in this graph are connected to monomials in $J$.
If not, the connection is explained in the proof of the next theorem.
\begin{proposition}
    Let $d$ be the largest integer such that $s_n(d) \neq 0$, i.e. the size of the largest independent set in $G_n$.
    Then
    \begin{equation*}
        \dim(\Gr(2, n)) = d - 1
    \end{equation*}
    and
    \begin{equation*}
        \deg(\Gr(2, n)) = s_n(d)
    \end{equation*}
\end{proposition}
\begin{proof}
    The idea is to apply Macaulay's basis theorem to get information about the Hilbert function of the Grassmanian.
    To this end, observe that all the monomials generating $\mathrm{lt}(\I(\Gr(2, n)))$ are square-free.
    Hence, we can partition all monomials not in $\mathrm{lt}(\I(\Gr(2, n)))$ into sets depending on which variables occur in them.
    Doing this shows that leading coefficient of the Hilbert polynomial depends only on the groups with the maximal count of monomials.
    These monomials then form a maximal independent set in $G_n$, which allows us to relate degree and dimension of $\Gr(2, n)$ to $s_n(d)$.
